Home

### 2021-02-19 analysis/index.Rmd
workflowr::wflow_publish("analysis/index.Rmd")

[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.6.0-brightgreen.svg)](https://cran.r-project.org/) [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2582969.svg)](https://doi.org/10.5281/zenodo.2582969)

>>>>

[![minimal R version](https://img.shields.io/badge/R%3E%3D-4.0.3-brightgreen.svg)](https://cran.r-project.org/) [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.2582969.svg)](https://doi.org/10.5281/zenodo.2582969)
